Hector Permafrost

### 2019-06-04 analysis/paper/paper.Rmd
Render large figures separately
This saves them having to be redrawn every time I fix something in the
paper file. The redrawing process takes forever.

---
title: "Hector Permafrost"
author:
  - Alexey N. Shiklomanov
  - Ben Bond-Lamberty
  - Ben Kravitz?
  - Kate Calvin?
  - Corinne Hartin
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx"
    rmarkdown::github_document:
      html_preview: false
bibliography: ["references.bib", "packages.bib"]
csl: "../templates/biogeosciences.csl"
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

@@

```{r fig-global-dist, fig.cap = global_dist_cap}
global_dist_cap <- paste(
  "Input parameter distributions for global Hector."
)
readd(draws_global_sims)
```

@@

```{r fig-biome-dist, fig.cap = biome_dist_cap, fig.dim = c(9, 9)}
biome_dist_cap <- paste(
  "Input parameter distributions for global Hector."
)
readd(draws_biome_sims)
```

>>>>

---
title: "Hector Permafrost"
author:
  - Alexey N. Shiklomanov
  - Ben Bond-Lamberty
  - Ben Kravitz
  - Corinne Hartin
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx"
    rmarkdown::github_document:
      html_preview: false
bibliography: ["references.bib", "packages.bib"]
csl: "../templates/biogeosciences.csl"
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

@@

```{r fig-global-dist, fig.cap = global_dist_cap}
global_dist_cap <- paste(
  "Input parameter distributions for global Hector."
)
# readd(draws_global_sims)
knitr::include_graphics(file_in(here::here("analysis", "figures", "global_draws.png")))
```

@@

```{r fig-biome-dist, fig.cap = biome_dist_cap, fig.dim = c(9, 9)}
biome_dist_cap <- paste(
  "Input parameter distributions for global Hector."
)
# readd(draws_biome_sims)
knitr::include_graphics(file_in(here::here("analysis", "figures", "biome_draws.png")))
```
